An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-21 draft.tex
Bigger Figures
New Figuares can be seen when printed. Using 12 points  font.
Comp iniciated

\usepackage{lineno,hyperref}
\graphicspath{ {./images/} }

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{kafkEOsmall}
    \caption{The proposed general architecture, 
     showing each process in a swimlane, message-dataflow,
     message queues, and high-level tasks for each process.} % This caption? - JJ
    \label{fig:kafkEO}
\end{figure}

@@

@@

@@

\subsection{Comparison} 
\label{edm}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{classicisland}
    \caption{ Population State and dataflow between processing nodes of a classic Island-based multi-population algorithm. }
    \label{fig:classicisland}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{pool_island}
    \caption{Population State and dataflow between processing nodes of a Pool-based multi-population algorithm.}
    \label{fig:pool_island}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{population_pool}
    \caption{Population State and dataflow between processing nodes of the EvoSpace algorithm.}
    \label{fig:population_pool}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{population_message}
    \caption{Population State and dataflow between processing nodes of the EvoSpace algorithm.} % Er, same caption. Better insert it now, or we might roftet... Also, same label. - JJ
    % Ok, it was a "temporal" Copy-Paste solution - Mario
    \label{fig:population_message}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{experiment_flow}
    \caption{EvoSwarm Workflow}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{worker}
    \caption{Serverless function implementation details. Showing the worker algorithm in each container}
\end{figure}

>>>>

\usepackage{lineno,hyperref}
\usepackage{rotating}
\graphicspath{ {./images/} }

@@

\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{kafkEOsmall}
    \caption{The proposed general architecture, 
     showing each process in a swimlane, message-dataflow,
     message queues, and high-level tasks for each process.} % This caption? - JJ
    \label{fig:kafkEO}
\end{sidewaysfigure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{population_message}
    \caption{Population State and dataflow between processing nodes of a message-based algorithm.}
    \label{fig:population_message}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{classicisland}
    \caption{ Population State and dataflow between processing nodes of a classic Island-based multi-population algorithm. }
    \label{fig:classicisland}
\end{figure}

\subsection{Comparison} 
\label{comparison}

Next, we compare the message-driven architecture we presented against four other
proposals for multi-population algorithms found in the literature. We center the
comparison on the coupling and communication between the main components:
Subpopulations, Processing Nodes, and Algorithms.  In Figure \ref{fig:population_message} we show the
main components of a message-driven architecture. We can see that the algorithm
and the subpopulations are separated, and the Population Queue keeps the state
of subpopulations. While algorithms only need the subpopulations as parameters
for their execution.  In contrast, in the classic Island model shown in Figure
\ref{fig:classicisland}, algorithms are coupled with a subpopulation, and the same processing
node keeps both the algorithm process and the state of the subpopulation.  Other
processing nodes follow the same configuration and form of execution, and they
only pass specific individuals between them.  In this model, adding additional
processing nodes, on-runtime, can be more difficult, because they need to have
an addressing mechanism. % JJ, help I don't know if this is clearly understood, a mean like a DNS - Mario

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{pool_island}
    \caption{Population State and dataflow between processing nodes of a Pool-based multi-population algorithm.}
    \label{fig:pool_island}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{population_pool}
    \caption{Population State and dataflow between processing nodes of the EvoSpace algorithm.}
    \label{fig:population_pool}
\end{figure}

@@

@@

\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{experiment_flow}
    \caption{EvoSwarm Workflow}
\end{sidewaysfigure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{worker}
    \caption{Serverless function implementation details. Showing the worker algorithm in each container}
\end{figure}
